### 2013-06-30 doc/pgas13/evaluation.tex

\paragraph{Connected Components.}
\begin{figure}[t]
  \centering
  \includegraphics[width=0.38\textwidth]{data/plots/cc_perf.pdf}
  \caption{\emph{Connected Components} on the same scale 26 Graph500 graph. Performance is measured in MTEPS.}
  \label{fig:cc_perf}
\end{figure}
Connected Components (CC) is another simple graph analysis kernel that illustrates a different use of global data structures in irregular applications. We implement the three-phase CC algorithm~\cite{mtgl} which was designed for the massively parallel MTA-2 machine. In the first phase, parallel traversals attempt to claim vertices and label them.
Whenever two traversals encounter each other, an edge between the two roots is inserted in a set. 
% After all edges have been traversed in this way, the set of edges forms a new, typically much smaller, graph.
The second phase performs the classical Shiloach-Vishkin parallel algorithm~\cite{shiloach1982n} on the reduced graph formed by the edge set from the first phase, and the final phase propagates the component labels out to the full graph.
Creation of the reduced edge set dominates the runtime of this algorithm, but includes many repeated inserts at the boundary between traversals, so is a prime target for the flat-combining Set.
Similar to BFS, the Set is write-only first, then read-only later, so further optimizations involving relaxation of consistency can be applied. Therefore, we compare our straightforward implementation using the generic Set with and without flat combining against a tuned asynchronous implementation.

>>>>

\paragraph{Connected Components.}
\begin{figure}[t]
  \centering
  \includegraphics[width=0.38\textwidth]{data/plots/cc_perf.pdf}
  \caption{\emph{Connected Components} on the same scale 26 Graph500 graph. Performance is measured in MTEPS.}
  \label{fig:cc_perf}
\end{figure}
Connected Components (CC) is another core graph analysis kernel that illustrates a different use of global data structures in irregular applications. We implement the three-phase CC algorithm~\cite{mtgl} which was designed for the massively parallel MTA-2 machine. In the first phase, parallel traversals attempt to claim vertices and label them.
Whenever two traversals encounter each other, an edge between the two roots is inserted in a set. 
% After all edges have been traversed in this way, the set of edges forms a new, typically much smaller, graph.
The second phase performs the classical Shiloach-Vishkin parallel algorithm~\cite{shiloach1982n} on the reduced graph formed by the edge set from the first phase, and the final phase propagates the component labels out to the full graph.
Creation of the reduced edge set dominates the runtime of this algorithm, but includes many repeated inserts at the boundary between traversals, so is a prime target for the flat-combining Set.
Similar to BFS, the Set is write-only first, then read-only later, so further optimizations involving relaxation of consistency can be applied. Therefore, we compare our straightforward implementation using the generic Set with and without flat combining against a tuned asynchronous implementation.

### 2013-06-30 doc/pgas13/grappa.tex

Highly tuned implementations of irregular applications in shared-memory, PGAS and message-passing paradigms, typically end up implementing similar constructs. Grappa includes these as part of its core infrastructure and simply asks the programmer to express concurrency which it can leverage to provide performance.

Grappa's programming interface, implemented as a C++11 library, provides high-level operations to access and synchronize through global shared memory, and task and parallel loop constructs for expressing concurrency. In addition, the Grappa ``standard library'' includes functions to manipulate a global heap, stock remote synchronization operations such as \emph{compare-and-swap}, and several synchronized global data structures. The following sections will explain the execution model of Grappa and the current C++ programming interface.

>>>>

Highly tuned implementations of irregular applications in shared-memory, PGAS, and message-passing paradigms, typically end up implementing similar constructs. Grappa includes these as part of its core infrastructure and simply asks the programmer to express concurrency which it can leverage to provide performance.

Grappa's programming interface, implemented as a C++11 library, provides high-level operations to access and synchronize through global shared memory, and task and parallel loop constructs for expressing concurrency. In addition, the Grappa ``standard library'' includes functions to manipulate a global heap, stock remote synchronization operations such as \emph{compare-and-swap}, and several synchronized global data structures. These features make it suitable for implementing some next-generation PGAS languages like Chapel~\cite{chapel} and X10~\cite{x10}. The following sections will explain the execution model of Grappa and the current C++ programming interface.

### 2013-06-30 doc/pgas13/relatedwork.tex

Our work extends the flat-combining paradigm further, to the PGAS domain, where only software provides the illusion of a physically distributed memory. The relatively higher cost of communication in PGAS makes flat combining even more compelling. In addition, the physical isolation per node combined with Grappa's engineered per-core isolation guarantees, create a novel situation for combining, which led to our \emph{combining proxy} design.

>>>>

Our work extends the flat-combining paradigm further, to the PGAS domain, where only software provides the illusion of global memory to physically distributed memories. The relatively higher cost of fine-grained data-driven access patterns in PGAS makes flat combining even more compelling. In addition, the physical isolation per node combined with Grappa's engineered per-core isolation guarantees, create a novel situation for combining, which led to our \emph{combining proxy} design.
